Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions

### 2022-12-19 latex/ackley_best_fits.tex
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Best Fits For Ackley Function}
\label{solutions:ackley}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     36 &      108 &      0.00 \\
 bfgs & $S_{2}$ &     42 &      129 &      0.00 \\
lbfgs & $S_{3}$ &     37 &      389 &      0.00 \\
  lma & $S_{4}$ &     38 &      320 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Ackley Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:ackley}:

\begin{table}[H]
\centering
\caption{Best Fits For Ackley Function}
\label{solutions:ackley}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     36 &      108 &      0.00 \\
 bfgs & $S_{2}$ &     42 &      129 &      0.00 \\
lbfgs & $S_{3}$ &     37 &      389 &      0.00 \\
  lma & $S_{4}$ &     38 &      320 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

The Ackley function has a narrow space around the optimal solution and,
although specially LMA is of rapid convergence, it iterated 38 times to find
the optimal value. All algorithms were very slow to converge and the most expensive
are LMA and LBFGS.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are of order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/ackley_convergence.tex
Initial Versioning of Article and Latex Builder

All algorithms converged 100 times, using 100 different initial solutions,
for a constrained search space of .$[-0.05, 0.05]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum.

>>>>

All algorithms converged 100 times, using 100 different initial solutions,
for a constrained search space of $\left[-0.05, 0.05\right]$ . This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Ackley Function has a well defined valley that has the solution as its center, as is shown in
Section~\ref{isolinesackley2D}.

### 2022-12-19 latex/beale_best_fits.tex
Initial Versioning of Article and Latex Builder

The Beale function has a very large search space around the optimal solution and
it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
BFGS/LBFGS performed as expected.

Altough the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

>>>>

The Beale function has a very large search space around the optimal solution and
it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
is surprisingly fast to find the solution. The LMA, known to be fast, had a reasonable performance.
BFGS/LBFGS performed as expected.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are of order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/beale_function_values.tex
Initial Versioning of Article and Latex Builder

LMA again had the worst performance. It is the only algorithm that, altiugh has some solutions in
poor convergence, that has a median greater than zero. LBFGS and DFP seems quite radical in terms
of convergence, while having a median of zero its mean values are greater than zero an its maximal
value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
and signifies that the algorithm don't fit very well for BEale Fnction minimum.

>>>>

LMA again had the worst performance. It is the only algorithm that, although has some solutions in
poor convergence, that has a median greater than zero. LBFGS and DFP seems quite radical in terms
of convergence, while having a median of zero its mean values are greater than zero an its maximal
value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
and signifies that the algorithm don't fit very well for the Beale Function minimum.

### 2022-12-19 latex/booth_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Beale Function}
\label{detailedsolutions:beale}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
$x_{2}$ &     0.50 &     0.50 &     0.50 &     0.50 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Beale Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:booth}, are shown
in Table~\ref{detailedsolutions:booth}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Booth Function}
\label{detailedsolutions:booth}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
\bottomrule
\end{tabular}
\end{table}

The optimal solution for Booth Function is $\left[1, 3\right]$ and the rounded values
of Table~\ref{detailedsolutions:booth} points to the same value. The error of
these values are of order $10^{-13}$ os less.

### 2022-12-19 latex/booth_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Ackley Function}
\label{convergence:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Booth Function is shown in Table~\ref{convergence:booth}:

\begin{table}[H]
\centering
\caption{Convergence Report For Booth Function}
\label{convergence:booth}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

All algorithms converged 100 times, using 100 different initial solutions,
for a constrained search space of $\left[0, 4\right]$ . This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Booth Function has a well defined valley that has the solution as its center, as it is shown
in Section~\ref{isolinesbooth2D}.

### 2022-12-19 latex/booth_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Statistical Information about function values For Ackley Function}
\label{function_values:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:beale}:

\begin{table}[H]
\centering
\caption{Statistical Information about function values For Booth Function}
\label{function_values:booth}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Booth Function.

### 2022-12-19 latex/header.tex
Initial Versioning of Article and Latex Builder

\begin{itemize}
	\item \textit{Convergence: } the convergence of an algorithm is classified as good, por and divergence.
	\subitem \textit{Good convergence: } the final solution is really near the optimal solution within the max iterations;
	\subitem \textit{Poor convergence: } the final solution is far from the optimal solution for any reason;
	\subitem \textit{Divergence: }  the final solution is out of the funtion's search space;
	\item \textit{Statistical Parameters about the solutions:} Mean and Median of the solutions are analysed to provide insights about the algorithms;
	\item Iterations to converge, function evaluations and function values.
\end{itemize}

>>>>

\begin{itemize}
	\item \textit{Convergence: } the convergence of an algorithm is classified as \textit{good}, \textit{poor} and \textit{divergence}.
	\subitem \textit{Good convergence: } the final solution is really near the optimal solution within the max iterations;
	\subitem \textit{Poor convergence: } the final solution is far from the optimal solution for any reason;
	\subitem \textit{Divergence: }  the final solution is out of the function's search space;
	\item \textit{Statistical Parameters about the solutions:} Mean and Median of the solutions are analysed to provide insights about the algorithms;
	\item Iterations to converge, function evaluations and function values.
\end{itemize}

### 2022-12-19 latex/matyas_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                                        Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp &   1.7926757117875478e-11,1.7863785568107216e-11 &           7 &                    10 &    1.281062e-23 \\
     bfgs & -4.0285184756435043e-19,-4.0615726129211233e-19 &           7 &                    10 &    6.547689e-39 \\
    lbfgs &   -3.837208328860697e-15,4.6629367034256575e-15 &           4 &                    16 &    1.806993e-29 \\
      lma &   3.5389027698051246e-06,3.5389027799876804e-06 &          14 &                    15 &    5.009533e-13 \\
\bottomrule
\end{tabular}

>>>>

The best solutions of all algorithms for Booth Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:matyas}:

\begin{table}[H]
\centering
\caption{Best Fits For Matyas Function}
\label{solutions:matyas}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      7 &       10 &      0.00 \\
 bfgs & $S_{2}$ &      7 &       10 &      0.00 \\
lbfgs & $S_{3}$ &      4 &       16 &      0.00 \\
  lma & $S_{4}$ &     14 &       15 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

The algorithms DFP, BFGS and LBFGS have comparable performances, while LMA
is the most expensive of all.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/matyas_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Booth Function}
\label{detailedsolutions:booth}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Matyas Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:matyas}, are shown
in Table~\ref{detailedsolutions:matyas}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Matyas Function}
\label{detailedsolutions:matyas}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

The optimal solution for Matyas Function is $\left[0, 0\right]$ and the rounded values
of Table~\ref{detailedsolutions:matyas} points to the same value. The error of
these values are of order $10^{-13}$ os less.

### 2022-12-19 latex/matyas_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Booth Function}
\label{convergence:booth}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Matyas Function is shown in Table~\ref{convergence:matyas}:

\begin{table}[H]
\centering
\caption{Convergence Report For Matyas Function}
\label{convergence:matyas}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

All algorithms converged 100 times, using 100 different initial solutions,
for a search space of $\left[-10, 10\right]$ . In this search space,
Matyas Function has a well defined valley that has the solution as its
center, as it is shown in Section~\ref{isolinesmatyas2D}.

### 2022-12-19 latex/rastrigin2d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                                       Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & -1.3945825916973396e-12,1.3762564161053067e-12 &           6 &                    11 &             0.0 \\
     bfgs &  4.190758074827946e-12,-2.1862133845293774e-11 &           8 &                    49 &             0.0 \\
    lbfgs &  8.784224615873606e-12,-3.6460273411768743e-11 &           5 &                   133 &             0.0 \\
      lma &  2.6660763338975985e-10,1.5611908894664897e-09 &           4 &                     5 &             0.0 \\
\bottomrule
\end{tabular}

>>>>

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin2d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin2d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      6 &       11 &      0.00 \\
 bfgs & $S_{2}$ &      8 &       49 &      0.00 \\
lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rastrigin in 2 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function much more times than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin2d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Matyas Function}
\label{detailedsolutions:matyas}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Rastrigin Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin2d}, are shown
in Table~\ref{detailedsolutions:rastrigin2d}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

The Table~\ref{detailedsolutions:rastrigin2d} shows the same solution to all algorithms, because the values are so small
and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rastrigin2d_convergence.tex
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &    99 &     1 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin2d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &    99 &     1 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

It is quite sure that all algorithms has good convergence for any algorithm for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center, as is shown in
Section~\ref{isolinesrastrigin2D}.

### 2022-12-19 latex/rastrigin2d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{lrrrr}
\toprule
Algorithm &  Minimal &      Maximum &         Mean &       Median \\
\midrule
      dfp &      0.0 & 1.492140e-13 & 1.186606e-14 & 0.000000e+00 \\
     bfgs &      0.0 & 0.000000e+00 & 0.000000e+00 & 0.000000e+00 \\
    lbfgs &      0.0 & 1.989918e+00 & 1.989918e-02 & 0.000000e+00 \\
      lma &      0.0 & 3.552714e-15 & 1.882938e-15 & 3.552714e-15 \\
\bottomrule
\end{tabular}

>>>>

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin2d}:

\begin{table}[H]
\centering
\caption{Statistical Information about function values For Rastrigin Function}
\label{function_values:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 1.99 &  0.02 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rastrigin Function.
Although the mean of LBFGS algorithm is greater than zero, it is expected
to converge mora than diverge in the function constrained search space.

### 2022-12-19 latex/rastrigin30d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin2d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      6 &       11 &      0.00 \\
 bfgs & $S_{2}$ &      8 &       49 &      0.00 \\
lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin30d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin30d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      8 &       14 &      0.00 \\
 bfgs & $S_{2}$ &      9 &       54 &      0.00 \\
lbfgs & $S_{3}$ &      6 &      135 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rastrigin in 30 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function twice than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin30d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Matyas Function}
\label{convergence:matyas}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin30d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

It is quite sure that all algorithms has good convergence for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center.

### 2022-12-19 latex/rastrigin4d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 7.824099927923849e-11,-2.1366231163644037e-10,-... &          10 &                    21 &             0.0 \\
     bfgs & 5.405272390841542e-12,-2.7239120065655507e-11,-... &          11 &                    61 &             0.0 \\
    lbfgs & 1.471102762075013e-10,1.9145855829354901e-10,8.... &           5 &                   133 &             0.0 \\
      lma & 2.6660763338975985e-10,1.5611908894664897e-09,-... &           4 &                     5 &             0.0 \\
\bottomrule
\end{tabular}

>>>>

The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rastrigin4d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin4d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     10 &       21 &      0.00 \\
 bfgs & $S_{2}$ &     11 &       61 &      0.00 \\
lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rastrigin in 4 dimensions, while LBFGS
is the most expensive of all. Although it has one more iteration than LMA, it evaluates
the objective function twice than BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin4d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Rastrigin Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin4d}, are shown
in Table~\ref{detailedsolutions:rastrigin4d}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{3}$ &    -0.00 &    -0.00 &     0.00 &    -0.00 \\
$x_{4}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

The Table~\ref{detailedsolutions:rastrigin4d} shows the same solution to all algorithms, because the values are so small
and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rastrigin4d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rastrigin Function in 4 dimensions is shown in Table~\ref{convergence:rastrigin4d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

It is quite sure that all algorithms has good convergence for any algorithm for a
constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
the optimal solution to avoid wrong convergence to a local minimum. In this search space,
Rastrigin Function has a well defined valley that has the solution as its center.

### 2022-12-19 latex/rosenbrock2d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                              Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 0.9999999999008999,0.9999999997978861 &          24 &                    31 &    1.135257e-20 \\
     bfgs &                1.0,0.9999999999999999 &          30 &                    43 &    1.232595e-30 \\
    lbfgs & 0.9999999994699225,0.9999999989299816 &          27 &                    76 &    2.907107e-19 \\
      lma & 0.9999999979097256,0.9999999958107717 &          16 &                    18 &    4.376780e-18 \\
\bottomrule
\end{tabular}

>>>>

The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock2d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock2d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     24 &       31 &      0.00 \\
 bfgs & $S_{2}$ &     30 &       43 &      0.00 \\
lbfgs & $S_{3}$ &     27 &       76 &      0.00 \\
  lma & $S_{4}$ &     16 &       18 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rosenbrock Function in 2 dimensions, while LBFGS
is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
the objective function twice as much of BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock2d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{3}$ &    -0.00 &    -0.00 &     0.00 &    -0.00 \\
$x_{4}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Rosenbrock Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock2d}, are shown
in Table~\ref{detailedsolutions:rosenbrock2d}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

The optimal point of Rosenbrock function in 2 dimensions is correctly pointed to $\left[1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock2d}
shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
